\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage[margin=20mm]{geometry}
\usepackage{color}

\newcommand{\todo}[1]{{\color{blue} TODO[#1]}}

\begin{document}

\title{5DV152/VT15: Lab 5}
\author{\todo{Your Name} (\todo{Your Personnumber})}
\date{\todo{Submission Date}}
\maketitle


\section{Study technique}

\begin{itemize}
\item Describe how you studied the article.
\item Described your participation in the seminar.
\end{itemize}

\section{Explanation of Steps P1-P3}

\begin{itemize}
\item Explain Steps P1-P3 using your own words.
\item Include a small but not trivial example.
\end{itemize}

\section{The three phases of the parallelized join}

\begin{itemize}
\item Informally explain the three phases of the parallelized join using your own words.
\item Try to explain the motivation behind each phase.
\end{itemize}

\section{The bandwidth-oblivious sort}

\begin{itemize}
\item Explain the bandwidth-oblivious sort algorithm using your own words.
\item Include an illustration that captures the essence of the algorithm.
\end{itemize}

\section{Reflection}

\begin{itemize}
\item Reflect on your learning experience in this lab.
\item What was it like to study the article in depth? What was the main challenge for you? 
\item How did your participation in the seminar affect your understanding of the article?
\item What did you learn while writing this report?
\end{itemize}

  
\end{document}
